Analysis

### 2022-01-27 code/R/Analysis.Rmd
Added some analyses of ground truth tracks

nyaa04_meta %>% 
ggplot()+
  geom_point(aes(x = flower_start, y = flower_length))

@@

nyaa04 %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(Class)), size = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("NYAA-04 Ground Truth") +
  theme(legend.position = "none")
```

@@

@@

>>>>

nyaa04_meta %>% 
ggplot()+
  geom_point(aes(x = flower_start, y = flower_length, colour = Class))

@@

nyaa04xx = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/_parameterTest_NYAA-04_3/parameterTest_NYAA-04_maxDisap_10_runMean_10_maxDist_300.csv")

nyaa04xx %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(objectID)), size = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("NYAA-04 Tracked (xx)")  +
  theme(legend.position = "none")

nyaa04 %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(Class)), size = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("NYAA-04 Ground Truth") +
  theme(legend.position = "none")

#nyaa04_meta %>% 
#  ggplot() +
#  geom_point(aes(x = DOY, y = Class))

@@

```
Largest gap in time

```{r}
x = nyaa04_meta %>%
    group_by(Class) %>%
    arrange(time) %>%
    mutate(diff = time - lag(time, default = first(time)))

x = nars13_meta %>%
    group_by(Class) %>%
    arrange(time) %>%
    mutate(diff = time - lag(time, default = first(time)))

# NYAA-04: 5.1
# NARS-13: 1.25

@@

Largest gap in number of frames

x = nyaa04 %>% 
  mutate(frame = as.integer(str_remove(str_extract(FileName, regex("\\d{6}")), "^0+"))) %>% 
  group_by(Class) %>%
  arrange(frame) %>%
  mutate(diff = frame - lag(frame, default = first(frame)))
